```{r}
library(dplyr)

data <- "https://raw.githubusercontent.com/fivethirtyeight/data/master/college-majors/majors-list.csv"
majors <- read.csv(data, stringsAsFactors = FALSE)

filtered_majors <- majors %>%
  filter(grepl("DATA|STATISTICS", Major, ignore.case = TRUE))

filtered_majors
```

```{r}
fruits_vegetables <- c("bell pepper", "bilberry", "blackberry", "blood orange", "blueberry", "cantaloupe", "chili pepper", "cloudberry", "elderberry", "lime", "lychee", "mulberry", "olive", "salal berry")

cat(paste0("c(", paste(shQuote(fruits_vegetables, type = "cmd"), collapse = ", "), ")"))
```

(.)\1\1
This expression matches any character that is repeated three times.

"(.)(.)\\2\\1"
This expression matches if two characters are repeated backwards after the first two. A four letter or symbol palindrome. Example: xyyx

(..)\1
This expression matches if two characters are repeated identically.

"(.).\\1.\\1"
This expression matches the placement of the first character if it appears third and fifth in a string. 

"(.)(.)(.).*\\3\\2\\1"
This expression matches if three characters are found in reverse order at the end of a string. The characters and the number of characters inbetween do not matter if the last three are the same as the first three reversed. 

```{r}
words <- c("radar", "level", "hello", "world", "a", "racecar")
pattern <- "^(.).*\\1$"
matches <- grepl(pattern, words)
words[matches]
```

```{r}
words1 <- c("salsa", "mama", "world", "hello", "banana")
pattern_w <- "(..).*\\1"
matches1 <- grepl(pattern_w, words1)
words1 [matches1]
```

```{r}
words2 <- c("seventy", "ethereal", "surprises", "other", "masks")
pattern2 <- "(.).*\\1.*\\1"
matches2 <- grepl(pattern2, words2)
words2 [matches2]
```

```{r}
words3 <- c("abcdeffedcba", "000abc000abc", "000abc000", "dada")
pattern3 <- "(.)(.)(.).*\\3\\2\\1"
matches3 <- grepl(pattern3, words3)
words3[matches3]
```


